main_analyses_prereg

### 2021-04-28 analysis/step4_main_analyses/examine_photodraw_classifications.Rmd
move starter analysis scripts to new folder

---
title: "Examine_classifications"
author: "Bria Long"
date: "4/9/2021"
output: html_document
---

@@

## Load compiled classification data
```{r load-classifications}
classification_data <- read.csv('compiled_classifications/Classification_Outputs2832.csv') %>%
  as.tibble() %>%
  # mutate(session_id = paste('cdm_',session_id,sep="")) %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>% 
  # mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X) %>%
  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(site = as.factor(site))
```

## Need to rewrite some code to get meta-data for couchdb/mongodb dumps
```{r}
## Load in meta data from mongo-db database dumps
# metadata_photodraw <- read.csv('mongodb-output/Photodraw2_AllDescriptives_1475_images_final_CDM_photodraw_e2_no_blanks.csv') %>%
#   as.tibble() %>%
#   mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
#   mutate(session_id = as.factor(session_id)) %>%
#   mutate(draw_duration_new = replace(draw_duration_new, draw_duration_new > 30,30))
# 
# ## join with classification data
# d <- classification_data %>%
#   left_join(metadata_photodraw) %>%
#   mutate(age_numeric = as.numeric(str_split_fixed(age,'age',2)[,2]))
```

## Read in meta data fed to classifications
```{r}
meta <- read_csv(here('data/compiled/meta/METADATA_kid.csv'))
```

## Compile some sanity checks on counts of draiwngs per site/condition/etc
```{r}
sanity_counts <- classification_data %>%
  left_join(meta, by=c('session_id' = 'session', 'category' = 'label')) %>%
  filter(age_numeric < 10) %>%
  group_by(condition,age_numeric, site) %>%
  summarize(num_drawings = n()) %>%
  kable()
```

@@

count_by_category <- d %>%
  group_by(category) %>%
  summarize(num_drawings = length(unique(session_id)), what = length(unique(index)))

what <- d %>%
  group_by(index) %>%
  summarize(num_ids = length(session_id)) %>%
  filter(num_ids >1)

@@

265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum & Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area. We aimed to recruit approximately 120 children aged 4-9 years of age after exclusions (i.e. 20 4-year-olds, 20 5-year-olds). In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, leading to a final sample of `r count_by_site$num_participants[1]` children. In the China based sample, 140 children participated; (10) participants were tested but their data was not recorded due to a technical error with the remote database, leading to a final sample of `r count_by_site$num_participants[2]`. A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.

@@

# Descriptive anlayses
```{r descriptives-across-age}
### How do our covariates change with age? Compute means and CIs; Group by age/category
## first join  data  
d <- classification_data %>% 
  left_join(meta, by=c('session_id' = 'session', 'category' = 'label'))

```{r}
cor_by_age <- d %>%  
  group_by(session_id,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") 
```

>>>>

---
title: "Examine_photodraw_classifications"
author: "Bria Long"
date: "4/2021"
output: html_document
---

@@

## Load compiled classification data
```{r load-classifications}
classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2832.csv')) %>%
  as_tibble() %>%
  # mutate(session_id = paste('cdm_',session_id,sep="")) %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>% 
  # mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X, -X.1, -index) %>%
  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(site = as.factor(site))
```

## Get drawing-specific metadata and join with main dataset
```{r}
## Load in meta data from mongo-db database dumps
CDM_metadata <- read.csv(here::here('data/CDM/drawing_metadata/Photodraw2_CDM_AllDescriptives_1922_images_final_CDM_photodraw_e2.csv')) %>%
  as_tibble() %>%
  mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
  mutate(session_id = as.factor(session_id)) %>%
  mutate(draw_duration = replace(draw_duration_new, draw_duration_new > 30,30)) %>%
  select(session_id, condition, category, num_strokes, draw_duration, mean_intensity)

# for THU
```{r}
THU_final_subject_info = read_csv(here::here('data/THU/demographics/final_subject_info.csv')) %>%
  as_tibble() %>%
  select(ID_Database_raw, ID_Database) %>%
  rowwise() %>%
  mutate(ID_Database_raw = str_replace_all(ID_Database_raw, fixed(" "), "")) %>%
  mutate(ID_Database_raw = as.factor(ID_Database_raw)) %>%
  rename(session_id = ID_Database) #session_id = cleaned ID_Database anme for merging with CDM data

all_THU_metadata<- read.csv(here::here('data/THU/drawing_metadata/THU_Drawings_AllDescriptives_april2021_all.csv')) %>%
  select(subid, condition, category, num_strokes, draw_duration, mean_intensity, filename) %>%
  rowwise() %>%
  mutate(ID_Database_raw = str_replace_all(subid, fixed(" "), "")) %>% #subid = ID_Database_raw in this spreadsheet, I know, sorry
  mutate(ID_Database_raw = as.factor(ID_Database_raw))

# joint drawing metadata with subject info
THU_metadata <-  THU_final_subject_info %>%
  left_join(all_THU_metadata, by=c("ID_Database_raw")) %>%
  select(-ID_Database_raw, -subid, - filename)

# check nothing went wrong with merging
assert_that(sum(is.na(THU_metadata$num_strokes))==0)

### join both sets of metadata together
```{r}
all_meta <- CDM_metadata %>%
  full_join(THU_metadata)
```

### join with classification data -- which has age embedded
```{r}
d <- classification_data %>%
  left_join(all_meta, by=c('category','session_id'))  %>%
  mutate(age_numeric = as.numeric(str_split_fixed(age,'age',2)[,2])) %>%
  mutate(age_numeric = replace(age_numeric, age_numeric==10,9)) # two THU participants who are just barely 10-years old, including in 9-year-old group

# subids in d should be a superset of those in classification_data
check_ids <- classification_data %>%
  filter(!session_id %in% unique(all_meta$session_id))
assert_that(length(check_ids$age)==0) # all match up

### get rid of tech error drawings (see note)
```{r}
# bizarrely, there are 24 drawing for which stroke data didn't save -- technical error.
# this was checked directly in mongodb database -- no idea why, assuming bad internet.
tech_error_drawings <- d %>%
  filter(is.na(num_strokes))
# filter out terch error drawings from dataset (24)
d <- d %>%
  filter(!is.na(num_strokes)) 
```

```{r}
# only did one practice trial, not in subject log or classification data because no category level trials
missing_id <- CDM_metadata %>%
  filter(!session_id %in% d$session_id)
```

## Compile some sanity checks on counts of draiwngs per site/condition/etc
```{r}
sanity_counts <- d %>%
  group_by(condition,age_numeric, site) %>%
  summarize(num_drawings = n()) %>%
  kable()
```

@@

count_by_category <- d %>%
  group_by(category) %>%
  summarize(num_drawings = length(unique(session_id)))

@@

265 participants were recruited from the San Jose Children’s Discovery museum, the Palo Alto Junior Museum and Zoo, and preschool and elementary schools outside of Beijing; approximately equal numbers of participants were recruited in Northern California and the Beijing area. We aimed to recruit approximately 120 children between 4-9 years of age after exclusions (i.e. 20 4-year-olds, 20 5-year-olds, etc.). In the US-based sample, 135 children participated; 6 participants were excluded, (3) for skipping more than 6 trials, and (3) for scribbling three or more times in a row; (6) participants were tested but their data was not recorded due to a technical error, and (2) participants never made it past the practice trials, leading to a final sample of 121 children. In the China based sample, `r count_by_site$num_participants[2]` children participated; an additional 8 participants were tested but their data was not recorded due to a technical error with the remote database. Two 10-year-olds (aged 10 years, 0 months and 10 years, 1 month) were accidentally tested and included in the 9-year-old age group. A complete breakdown of the number of subjects in each age group and site can be found in the Appendix, Table 1A.

@@

# Descriptive anlayses
```{r descriptives-across-age}
### How do our covariates change with age? Compute means and CIs; Group by age/category
cor_by_age <- d %>%  
  group_by(session_id,category,condition,age_numeric, site) %>%
  summarize(avg_cor = mean(correct_or_not)) %>%
  group_by(age_numeric,condition, site) %>%
  multi_boot_standard(col = "avg_cor") 
```

### 2021-04-28 analysis/step4_main_analyses/main_analysis_for_prereg.Rmd
move starter analysis scripts to new folder

---
title: "Examine_photodraw_classifications"
author: "Bria Long"
date: "4/2021"
output: html_document
---

```{r, libraries}
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(langcog)
library(forcats)
library(egg)
library(gridExtra)
library(reticulate)
library(readr)
library(ggplot2)
library(reshape2)
library(lme4)
library(stringr)
library(viridis)
library(MuMIn)
library(here)
theme_set(theme_few())
```

## Load compiled classification data
```{r load-classifications}
classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2832.csv')) %>%
  as_tibble() %>%
  # mutate(session_id = paste('cdm_',session_id,sep="")) %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>% 
  # mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X, -X.1, -index) %>%
  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(site = as.factor(site))
```

## Get drawing-specific metadata and join with main dataset
```{r}
## Load in meta data from mongo-db database dumps
CDM_metadata <- read.csv(here::here('data/CDM/drawing_metadata/Photodraw2_CDM_AllDescriptives_1922_images_final_CDM_photodraw_e2.csv')) %>%
  as_tibble() %>%
  mutate(session_id = str_split_fixed(session_id,"_",2)[,2]) %>%
  mutate(session_id = as.factor(session_id)) %>%
  mutate(draw_duration = replace(draw_duration_new, draw_duration_new > 30,30)) %>%
  select(session_id, condition, category, num_strokes, draw_duration, mean_intensity)

# for THU
```{r}
THU_final_subject_info = read_csv(here::here('data/THU/demographics/final_subject_info.csv')) %>%
  as_tibble() %>%
  select(ID_Database_raw, ID_Database) %>%
  rowwise() %>%
  mutate(ID_Database_raw = str_replace_all(ID_Database_raw, fixed(" "), "")) %>%
  mutate(ID_Database_raw = as.factor(ID_Database_raw)) %>%
  rename(session_id = ID_Database) #session_id = cleaned ID_Database anme for merging with CDM data

all_THU_metadata<- read.csv(here::here('data/THU/drawing_metadata/THU_Drawings_AllDescriptives_april2021_all.csv')) %>%
  select(subid, condition, category, num_strokes, draw_duration, mean_intensity, filename) %>%
  rowwise() %>%
  mutate(ID_Database_raw = str_replace_all(subid, fixed(" "), "")) %>% #subid = ID_Database_raw in this spreadsheet, I know, sorry
  mutate(ID_Database_raw = as.factor(ID_Database_raw))

# joint drawing metadata with subject info
THU_metadata <-  THU_final_subject_info %>%
  left_join(all_THU_metadata, by=c("ID_Database_raw")) %>%
  select(-ID_Database_raw, -subid, - filename)

# check nothing went wrong with merging
assert_that(sum(is.na(THU_metadata$num_strokes))==0)

### join both sets of metadata together
```{r}
all_meta <- CDM_metadata %>%
  full_join(THU_metadata)
```

>>>>

---
title: "main_analyses_prereg"
author: "Bria Long"
date: "4/28/2021"
output: html_document
---

## Load compiled classification data

```{r load-classifications}
classification_data <- read.csv(here::here('data/compiled/compiled_classifications/Classification_Outputs2832.csv')) %>%
  as_tibble() %>%
  # mutate(session_id = paste('cdm_',session_id,sep="")) %>%
  mutate(age_numeric = age) %>%
  mutate(age = paste('age',age,sep="")) %>%
  mutate(age = as.factor(age)) %>%
  mutate(category = target_label) %>% 
  # mutate(image_name = paste(category,'_sketch_', age,'_', session_id,'.png',sep="")) %>%
  select(-X, -X.1, -index) %>%
  mutate(site = case_when( is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "THU", 
                           !is.na(str_locate(session_id,'photodraw_e2')[,1]) ~ "CDM")) %>%
  mutate(site = as.factor(site))
```
